### 2022-04-11 src/text/3-applications-subsections/3D-analysis.tex
some requested changes

@@

Starting from the \irfs corresponding to the same three simulated \cta observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset via the MapDatasetMaker. However, we will not use the simulated event lists provided by \cta but instead, use the method MapDataset.fake() to simulate measured counts from the combination of several SkyModel instances. In particular we simulate:
\begin{enumerate}
	\item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law spectral shape.
	\item An extended source with Gaussian morphology located at (l=0.4\textdegree, b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral shape.
	\item A large shell-like structure centered around (l=0.06\textdegree, b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree respectively and a power-law spectral shape.
\end{enumerate}
The position and sizes of the sources have been selected so that their contributions overlap. This can be clearly seen in the significance map shown in the left panel of Figure~\ref{fig:cube_analysis}. This map was produced with the ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a correlation radius of 0.1\textdegree.

We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters, which are in all cases well within 1$\sigma$ of the simulated parameters. We can now compute the residual significance map after removing the contribution from each model. This is done again via the ExcessMapEstimator. As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$.

>>>>

\cite{Mohrmann2019}

@@

Starting from the \irfs corresponding to the same three simulated \cta observations used in Section~\ref{ssec:1d-analysis}, we can create a MapDataset via the MapDatasetMaker. However, we will not use the simulated event lists provided by \cta but instead, use the method MapDataset.fake() to simulate measured counts from the combination of several SkyModel instances. In this way, a DL4 dataset can directly be simulated. In particular we simulate:
\begin{enumerate}
	\item A point source located at (l=0\textdegree, b=0\textdegree) with a power-law spectral shape.
	\item An extended source with Gaussian morphology located at (l=0.4\textdegree, b=0.15\textdegree) with $\sigma$=0.2\textdegree and a log-parabola spectral shape.
	\item A large shell-like structure centered around (l=0.06\textdegree, b=0.6\textdegree) with a radius and width of 0.6\textdegree and 0.3\textdegree respectively and a power-law spectral shape.
\end{enumerate}
The position and sizes of the sources have been selected so that their contributions overlap. This can be clearly seen in the significance map shown in the left panel of Figure~\ref{fig:cube_analysis}. This map was produced with the ExcessMapEstimator (see Section~\ref{ssec:gammapy-estimators}) with a correlation radius of 0.1\textdegree.

We can now fit the same model shapes to the simulated data and retrieve the best-fit parameters. To check the model agreement, we compute the residual significance map after removing the contribution from each model. This is done again via the ExcessMapEstimator. As can be seen in the middle panel of Figure~\ref{fig:cube_analysis}, there are no regions above or below 5$\sigma$, meaning that the models describe the data sufficiently well.
